Carbonate chemistry at Ny-Ålesund

### 2021-12-29 awipev-CO2.Rmd
minor

durPeriod <-  durPeriod %>%
  dplyr::arrange(datetime) %>%
  dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(durPeriod)])/2* 3600 )))%>%
  dplyr::mutate(dur_interval = datetime + middle[2:nrow(durPeriod)])

>>>>

durPeriod <-  durPeriod %>%
  dplyr::arrange(datetime) %>%
  dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(durPeriod)])/2* 3600 ))) %>%
  dplyr::mutate(dur_interval = datetime + middle[2:nrow(durPeriod)])
